Supplementary Materials

### 2024-10-18 pilot-publication/manuscript.Rmd
Update manuscript and supplementary materials

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
title: "Effect of Trauma Life Support Training on Patient Outcomes: A Pilot Cluster Randomised Trial"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    officedown::rdocx_document:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
#    md_document: default
#    bookdown::pdf_document2:
#      toc:false
#      number_sections:false
---

@@

**Main Outcomes and Measures** The feasibility outcomes were consent rate, lost to follow up rate, pass rate, missing data rates, and differences in distribution between observed and data extracted from medical records. The primary patient outcome was all cause mortality at 30 days from the time of arrival to the emergency department.

@@

The proprietary Advanced Trauma Life Support^®^ (ATLS^®^) and the low-cost alternative Primary Trauma Care (PTC) are the most established trauma life support training programmes with over a million physicians trained in over 80 countries [@acsAtls2018; @ptcfPtc2018]. Observational studies indicate that these programmes may improve patient outcomes [@Jin2021], but there is no high quality evidence from controlled trials to support this [@Mohammad2013; @Jayaraman2014; @Kadhum2020].

Several studies, including at least two randomised controlled trials [@Ali1996; @Ali1999], show that ATLS^®^ is associated with improved provider skills [@Mohammad2013]. Observational evidence indicates that PTC also leads to improved provider skills [@Kadhum2020]. The missing link is then how, and if, these improved skills translate into improved patient outcomes.

Systematic reviews call for trials in settings where these programmes are not routinely implemented, but data needed to inform the planning of such a trial is missing. We aimed to assess the feasibility of conducting a cluster randomised controlled trial comparing ATLS^®^ and PTC with standard care, and to estimate probable effect sizes and the intracluster correlation coefficient needed for the sample size calculations of a full-scale trial.

@@

## Standard Care
Standard care varies across hospitals in India, but most surgical and emergency medicine departments in India organise their physicians in units. These units typically include three faculty members and three to twelve residents, who are assigned a specific day of the week when they manage the emergency department. In the emergency department, trauma patients are initially assessed by first- or second-year residents who also resuscitate patients, perform interventions and refer patients for imaging or other investigations. Compared with other settings where a trauma team approach is adopted, nurses and other healthcare professionals are only involved to a limited extent during the initial management.

## Intervention
In each intervention arm the residents in one or two units were trained in either ATLS^®^ or PTC. For the purpose of this pilot study, our target was to train a minimum of 75% of residents in each unit. We did not train the units' faculty, because they are typically not directly involved in the initial management of trauma patients. The ATLS^®^ training was conducted in an ATLS^®^ certified training centre in Mumbai, according to the standard ATLS^®^ curriculum [@acsAtls2018]. The PTC training was conducted in New Delhi, according to the standard PTC curriculum [@ptcfPtc2018]. We did not modify or adapt the delivery or content of these programs during this pilot study.

@@

## Outcomes
We measured a large number of outcomes to help plan and assess the feasibility of a full scale trial. A complete list of outcomes is available as Supplementary Materials. Our main outcomes were:

@@

### Patients
Arriving patients were screened for eligibility and consented, if conscious. Unconscious patients were consented by the patient’s representative. This proxy consent was reaffirmed by the patient, on regaining consciousness. We followed up patients at 24 hours after arrival at the emergency department, and up to 30 days after arrival at the emergency department.

### Residents
Participating units were screened for eligibility once hospitals confirmed their participation. All residents in these units were approached to consent to training if their hospital was randomised to either of the intervention arms. The training was conducted approximately one month after the study started in that hospital.

## Sample size
We did not conduct a formal power calculation for this pilot study, as the primary aim was to assess the feasibility of the trial logistics and research methods. <!--The time period was dictated by budget and time constraints.-->

## Allocation and blinding
We used simple randomisation implemented using sealed envelopes to allocate sites to trial arms. We did not blind investigators, residents or patients to the interventions.

## Data Collection
Data was collected over a four-month period. A research officer collected data on all patients who presented on the days and shifts when participating residents were assigned to trauma care. The research officers observed care and interviewed residents and patients, and also extracted data from the hospital records. We followed up admitted patients for their complications and other in-hospital outcome measures. Patients who were not admitted were followed up telephonically for mortality outcomes and quality of life outcomes.

## Variables
The research officers collected data on demographics, time of injury to arrival at the participating hospital, time to recording vital signs, vital signs, times to and management details including imaging and surgery, and details of any injury sustained. For a subset of patients we also extracted data from medical records, to be able to compare the distribution of this data with the distribution of data collected through direct observations.<!--Supplemental Material 2 contains a full variable list, with definitions.-->

## Patient and public involvement
We conducted community consultations to collect inputs from patients, their caregivers, patient groups, and resident doctors to be used in the selection of outcome measures and implementation of the full-scale trial. The results of these consultations will be published separately.

@@

## Data monitoring
We conducted weekly online meetings to monitor the study and data collection. We conducted one interim analysis approximately halfway through the study, and decided to complete the study as residents and patients were consenting to be included in the study and key variables including mortality outcomes could be collected. We did not use a data monitoring committee.

## Statistical Methods
We analysed all data using descriptive statistics and did not perform any formal hypothesis tests [@Lee2014]. Quantitative variables are summarised as median and interquartile range. Qualitative variables are presented as absolute numbers and percentages. We used an empty generalised linear mixed model <!-- see [@Sommet2017] --> to estimate the intracluster correlation coefficient.

@@

Within each combination of trial arms we had planned to conduct subgroup analyses of men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly. These subgroups were however too small to allow for meaningful analyses, and are therefore reported descriptively.

<!--We calculated both absolute and relative differences for each
comparison, along with 75, 85, and 95% confidence intervals. We used an empirical bootstrap procedure with 1000 draws to estimate these confidence intervals.-->

## Ethics and Dissemination
We were granted research ethics approval from the institutional ethics committees at each participating hospital.

@@

The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`%, with details for selected variables shown in Table \@ref(tab:sample-characteristics) and in Supplementary Materials. The variables with the maximum amount of missing data were cause of death and some complications, reported in Supplementary Materials. The differences in distributions between observed data and data extracted from medical records, for selected variables that were collected through observation or interview, are shown in Table \@ref(tab:observed-vs-extracted). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

```{r observed-vs-extracted, echo = FALSE}
observed.vs.extracted.comparison.table %>%
  modify_caption("Differences in distributions between directly observed data and data extracted from medical records, for selected variables that were collected through observation or interview.")
```

After training, a total of `r m30d.standard.care` patients in the standard care arm died within 30 days, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The corresponding figures for in-hospital mortality were `r inhosp.standard.care`%, `r inhosp.atls`%, and `r inhosp.ptc`% for the standard care, ATLS and PTC arms respectively, as shown in Table \@ref(tab:outcomes). Overall, both in-hospital and 30-day mortality were substantially lower in the ATLS^®^ and PTC arms compared to the standard care arm, but the absolute numbers of deaths in the ATLS and PTC arms were very small. The results for all other outcomes are shown in Supplementary Materials.

```{r outcomes, echo = FALSE}
outcome.table.with.differences |>
  modify_caption("Mortality after training by the trial arms standard care, Advanced Trauma Life Support (ATLS) and Primary Trauma Care (PTC)")
```

# Discussion
We show that it is feasible to conduct and collect data for a cluster randomized controlled trial comparing ATLS^®^ with PTC and standard care. Missing data were low for key variables, including the primary outcome and many secondary outcomes. Some variables, especially cause of death and complications (reported in Supplementary materials) had very high missing data rates and may not be feasible to include in a full-scale trial, or require different data collection methods. The missing data was substantially higher when data was extracted from medical records instead of being directly observed, but the data were similarly distributed, indicating that data collected from medical records is reliable even if it is less complete.

@@

During the course of this pilot we deviated from the protocol in several ways, and provide a detailed list as Supplementary
material. Some key limitations of this pilot and therefore lessons to be learned and factored into the design of the full-scale trial include the lower than expected enrolment rates of some centres, centre specific management routines, and difficulties in collecting data on complications and cause of death.

@@

# Competing Interests
Several authors are ATLS^®^ and/or PTC instructors.

# Funding
Doctors for You through grants awarded to Karolinska Institutet by the Swedish Research Council (grant number 2020-03779) and the Laerdal Foundation (grant number 2021-0048).

# Data Sharing Statement
The final anonymized dataset and code for analysis are released publicly.

# Protocol Deviations

## Trial Registration
We intended to also register our trial with Clinical Trials Registry - India and will do so with the full-scale trial.

## Outcomes across subgroups
Because of small numbers in the pre-specified subgroups we decided to report only descriptive data on these subgroups.

## Number of Participating Centres
We ended up recruiting seven centres instead of six and therefore assigned two centres each to the intervention arms and three centres to the control arm.

## Resident Participants
Emergency medicine in addition to surgery.

## Periodic suverys to residents
We did not distribute periodic surveys to the participating residents but discussed challenges and suggestions that they had regarding the scheduling or implementation of the training programs.

## Follow up of residents
We stated that resident participants would be followed up 30 days after training, but revised this to follow them up after the end of the study period.

## Data collection from records
We decided to extract data from medical records only for a subset of patients to reduce the research officers' workload.

## Selection of units for training
We planned to use simple random sampling to select units if there were more than two eligible units in a hospital but instead the hospital principal investigator decided which units to train.

## Timing of resident consent
We had initially planned to ask residents for consent before
randomisation, but this was not possible because of logistical issues the units were only finalised after the hospitals had been randomised. Residents were therefore approached for consent after randomisation but before training.

## Analysis level of feasibility outcomes
We had planned to analyse feasibility outcomes on both an overall and individual cluster level, but we only analysed them on an overall level.

@@

# Supplementary material

>>>>

---
## compile with:
## Rscript -e "rmarkdown::render('manuscript.Rmd', output_format = 'all')"
## libreoffice --headless --convert-to pdf manuscript.docx
title: "Effect of Trauma Life Support Training on Patient Outcomes: A Pilot Cluster Randomised Trial"
author: Trauma life support training Effectiveness Research Network (TERN) collaborators
bibliography: bibliography.bib
csl: nature.csl
output:
    bookdown::word_document2:
      toc: false
      number_sections: false
      reference_docx: "reference.docx"
#    md_document: default
#    bookdown::pdf_document2:
#      toc:false
#      number_sections:false
---

@@

**Main Outcomes and Measures** The outcomes were consent rate, lost to follow up rate, pass rate, missing data rates, differences in distribution between observed and data extracted from medical records as well as all cause and in-hospital mortality at 30 days from the time of arrival to the emergency department.

@@

The proprietary Advanced Trauma Life Support^®^ (ATLS^®^) and the low-cost alternative Primary Trauma Care (PTC) are two widely established trauma life support training programmes with over a million physicians trained in over 80 countries [@acsAtls2018; @ptcfPtc2018]. Observational studies indicate that these programmes may improve patient outcomes [@Jin2021], but there is no high quality evidence from controlled trials to support this [@Mohammad2013; @Jayaraman2014; @Kadhum2020; putra_impact_2023].

Several studies, including at least two randomised controlled trials [@Ali1996; @Ali1999], show that ATLS^®^ is associated with improved provider skills [@Mohammad2013]. Observational evidence indicates that PTC also leads to improved provider skills [@Kadhum2020]. The missing link is then if these improved skills translate into improved patient outcomes.

Systematic reviews call for trials in settings where these programmes are not routinely implemented [@Jayaraman2014; @Kadhum2020], but data needed to inform the planning of such a trial is missing. We aimed to assess the feasibility of conducting a cluster randomised controlled trial comparing ATLS^®^ and PTC with standard care, and to estimate probable effect sizes and the intracluster correlation coefficient needed for the sample size calculations of a full-scale trial.

@@

## Standard Care

Standard care varies across hospitals in India, but most surgical and emergency medicine departments in India organise their physicians in units. These units typically include three faculty members and three to twelve residents, who are assigned a specific day of the week when they are posted in the emergency department. In the emergency department, trauma patients are initially assessed by first- or second-year residents who also resuscitate patients, perform interventions and refer patients for imaging or other investigations. Compared with other settings where a trauma team approach is adopted, nurses and other healthcare professionals are only involved to a limited extent during the initial management.

## Intervention

In each intervention arm the residents in one or two units were trained in either ATLS^®^ or PTC. For the purpose of this pilot study, our target was to train a minimum of 75% of residents in each unit. We did not train the units' faculty, because they are typically not directly involved in the initial management of trauma patients. The ATLS^®^ training was conducted in an ATLS^®^ certified training centre in Mumbai, according to the standard ATLS^®^ curriculum [@acsAtls2018]. The PTC training was conducted in New Delhi, according to the standard PTC curriculum [@ptcfPtc2018]. We did not modify or adapt the delivery or content of these programmes during this pilot study.

@@

We measured a large number of outcomes to help plan and assess the feasibility of a full scale trial. A list of outcomes is available in Supplementary Table S1. Our main outcomes were:

@@

Arriving patients were screened for eligibility and consented, if conscious. Unconscious patients were consented by the patient’s representative. This proxy consent was reaffirmed by the patient, on regaining consciousness. We followed up patients at 24 hours after arrival at the emergency department, and up to 30 days after arrival at the emergency department.

Participating units were screened for eligibility once hospitals confirmed their participation. All residents in these units were approached to consent to training if their hospital was randomised to either of the intervention arms. The training was conducted approximately one month after the study started in that hospital.

## Sample size

We did not conduct a formal power calculation for this pilot study, as the purpose was to assess the feasibility of the trial logistics and research methods. <!--The time period was dictated by budget and time constraints.-->

## Allocation and blinding

We used simple randomisation implemented using sealed envelopes to allocate sites to trial arms. We did not blind investigators, residents or patients to the interventions.

## Data Collection

Data was collected over a four-month period. A research officer collected data on all patients who presented on the days and shifts when participating residents were assigned to trauma care. The research officers observed care and interviewed residents and patients, and also extracted data from the hospital records. We followed up admitted patients for their complications and other in-hospital outcome measures. Patients who were not admitted were followed up telephonically for mortality outcomes and quality of life outcomes.

## Variables

The research officers collected data on demographics, time of injury to arrival at the participating hospital, time to recording vital signs, vital signs, times to and management details including imaging and surgery, and details of any injury sustained. For a subset of patients we also extracted data from medical records, to be able to compare the distribution of this data with the distribution of data collected through direct observations.<!--Supplemental Material 2 contains a full variable list, with definitions.-->

## Patient and public involvement

We conducted community consultations to collect inputs from patients, their caregivers, patient groups, and resident doctors to be used in the selection of outcome measures and implementation of the full-scale trial. The results of these consultations will be published separately.

@@

## Data monitoring

We conducted weekly online meetings to monitor the study and data collection. We conducted one interim analysis approximately halfway through the study, and decided to complete the study as residents and patients were consenting to be included in the study and key variables including mortality outcomes could be collected. We did not use a data monitoring committee.

## Statistical Methods

We analysed all data using descriptive statistics and did not perform any formal hypothesis tests [@Lee2014]. Quantitative variables are summarised as median and interquartile range. Qualitative variables are presented as absolute numbers and percentages. We used an empty generalised linear mixed model <!-- see [@Sommet2017] --> to estimate the intracluster correlation coefficient.

@@

Within each combination of trial arms we had planned to conduct subgroup analyses of men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly. These subgroups were however too small to allow for meaningful analyses, and are therefore reported descriptively.  We calculated both absolute and relative differences for each comparison, along with 75, 85, and 95% confidence intervals. We used an empirical bootstrap procedure with 1000 draws to estimate these confidence intervals.

In the interest of space, only the 95% confidence intervals are presented for all comparisons as Supplementary Tables. The remaining results are available from the corresponding author on request.

## Ethics and Dissemination

We were granted research ethics approval from the institutional ethics committees at each participating hospital.

@@

The percentage of patients who consented to follow up was `r p.consent`% and the percentage of residents who consented to training was `r recruitment.rate.residents`%. The lost to follow up rate was `r rate.lost.to.follow.up`%. The pass rate was `r pass.rate`%. The missing data rate ranged from `r min.missing.data` to `r max.missing.data`%, with details for selected variables shown in Table \@ref(tab:sample-characteristics) and in Supplementary Table S1. The variables with the maximum amount of missing data were complications, reported in Supplementary Tables S1-12. The differences in distributions between observed data and data extracted from medical records, for selected variables that were collected through observation or interview, are shown in Table \@ref(tab:observed-vs-extracted). Overall, the data were similarly distributed, but there were considerably more missing values in extracted data compared to observed data.

```{r observed-vs-extracted, echo = FALSE, tab.cap = "Differences in distributions between directly observed data and data extracted from medical records, for selected variables that were collected through observation or interview."}
observed.vs.extracted.comparison.table
```

After training, a total of `r m30d.standard.care` patients in the standard care arm died within 30 days, compared to `r m30d.atls` patients in the ATLS^®^ arm and `r m30d.ptc` patients in the PTC arm. The corresponding figures for in-hospital mortality were `r inhosp.standard.care`%, `r inhosp.atls`%, and `r inhosp.ptc`% for the standard care, ATLS and PTC arms respectively, as shown in Table \@ref(tab:outcomes). Overall, both in-hospital and 30-day mortality were substantially lower in the ATLS^®^ and PTC arms compared to the standard care arm, but the absolute numbers of deaths in the ATLS and PTC arms were very small. The results for all other outcomes are shown in Supplementary Tables S1-12.

```{r outcomes, echo = FALSE, tab.cap = "Mortality after training by the trial arms standard care, Advanced Trauma Life Support (ATLS) and Primary Trauma Care (PTC)"}
outcome.table.with.differences
```

# Discussion

We show that it is feasible to conduct and collect data for a cluster randomized controlled trial comparing ATLS^®^ with PTC and standard care. Missing data were low for key variables, including the primary outcome and many secondary outcomes. Some variables, especially complications (reported in Supplementary Table S1-12) had very high missing data rates and may not be feasible to include in a full-scale trial, or require different data collection methods. The missing data was substantially higher when data was extracted from medical records instead of being directly observed, but the data were similarly distributed, indicating that data collected from medical records is reliable even if it is less complete.

@@

During the course of this pilot we deviated from the protocol in several ways, and provide a detailed list as Supplementary
material S13. Some key limitations of this pilot and therefore lessons to be learned and factored into the design of the full-scale trial include the lower than expected enrolment rates of some centres, centre specific management routines, and difficulties in collecting data on complications and cause of death.

@@

# Competing Interests

Several authors are ATLS^®^ and/or PTC instructors.

# Funding

Doctors for You through grants awarded to Karolinska Institutet by the Swedish Research Council (grant number 2020-03779) and the Laerdal Foundation (grant number 2021-0048).

# Data Sharing Statement

The final anonymized dataset and code for analysis are released publicly.

@@

### 2024-10-18 pilot-publication/supplementary-materials.Rmd
Update manuscript and supplementary materials

@@

>>>>

# Table S1. Extended sample characteristics

```{r overall-table, echo = FALSE}
combined.sample.characteristics.table
```

@@

# S13 Protocol Deviations

## Trial Registration

We intended to also register our trial with Clinical Trials Registry - India and will do so with the full-scale trial.

## Outcomes across subgroups

Because of small numbers in the pre-specified subgroups men, women, blunt multisystem trauma, penetrating trauma, shock, severe traumatic brain injury, and elderly we decided to report only descriptive data on these subgroups.

## Number of Participating Centres

We recruited seven centres instead of six and therefore assigned two centres each to the intervention arms and three centres to the control arm.

## Resident Participants

We included emergency medicine residents in addition to surgical residents.

## Periodic suverys to residents

We did not distribute periodic surveys to the participating residents but discussed challenges and suggestions that they had regarding the scheduling or implementation of the training programs.

## Follow up of residents

We stated that resident participants would be followed up 30 days after training, but revised this to follow them up after the end of the study period.

## Data collection from records

We decided to extract data from medical records only for a subset of patients to reduce the research officers' workload.

## Selection of units for training

We planned to use simple random sampling to select units if there were more than two eligible units in a hospital but instead the hospital principal investigator decided which units to train.

## Timing of resident consent

We had initially planned to ask residents for consent before randomisation, but because of logistical issues the units were only finalised after the hospitals had been randomised. Residents were therefore approached for consent after randomisation but before training.

## Analysis level of feasibility outcomes

We had planned to analyse feasibility outcomes on both an overall and individual cluster level, but we only analysed them on an overall level, because the sample sizes in individual clusters were too small to generate meaningful results.

### 2024-10-18 pilot-publication/supplementary-outcome-tables.Rmd
Update manuscript and supplementary materials

# Results with 75% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

## Outcomes in all patients before training, by treatment arm

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients before training, by treatment arm"]]

## Outcomes in all patients after training, by treatment arm

outcome.results.tables[["ci.level.0.75"]][["Outcomes in all patients after training, by treatment arm"]]

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

outcome.results.tables[["ci.level.0.75"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

outcome.results.tables[["ci.level.0.75"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

outcome.results.tables[["ci.level.0.75"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

# Results with 85% confidence level

## Outcomes in all patients during the entire study period, by treatment arm

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients during the entire study period, by treatment arm"]]

## Outcomes in all patients before training, by treatment arm

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients before training, by treatment arm"]]

## Outcomes in all patients after training, by treatment arm

outcome.results.tables[["ci.level.0.85"]][["Outcomes in all patients after training, by treatment arm"]]

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

outcome.results.tables[["ci.level.0.85"]][["Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

outcome.results.tables[["ci.level.0.85"]][["Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms"]]

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with ATLS"]]

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing standard care with PTC"]]

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in outcomes after training, comparing ATLS with PTC"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC"]]

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

outcome.results.tables[["ci.level.0.85"]][["Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC"]]

@@

## Outcomes in all patients during the entire study period, by treatment arm

@@

## Outcomes in all patients before training, by treatment arm

@@

## Outcomes in all patients after training, by treatment arm

@@

## Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC

>>>>

@@

## Table S2 Outcomes in all patients during the entire study period, by treatment arm

@@

## Table S3 Outcomes in all patients before training, by treatment arm

@@

## Table S4 Outcomes in all patients after training, by treatment arm

@@

## Table S5 Absolute change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S6 Relative change from baseline for all outcomes, comparing the period after training with the period before training, by treatment arms

@@

## Table S7 Absolute and relative differences in outcomes after training, comparing standard care with ATLS

@@

## Table S8 Absolute and relative differences in outcomes after training, comparing standard care with PTC

@@

## Table S9 Absolute and relative differences in outcomes after training, comparing ATLS with PTC

@@

## Table S10 Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with ATLS

@@

## Table S11 Absolute and relative differences in changes from baseline for all outcomes, comparing standard care with PTC

@@

## Table S12 Absolute and relative differences in changes from baseline for all outcomes, comparing ATLS with PTC
